Untitled

### 2024-01-29 MSR.rmd
Update

@@

>>>>

```{r, include=FALSE, echo=FALSE, warning=FALSE, message = FALSE}
#                      -=( Install & Load Package Function )=-
install_load <- function (package1, ...)  {

   # convert arguments to vector
   packages <- c(package1, ...)

   # start loop to determine if each package is installed
   for(package in packages){

       # if package is installed locally, load
       if(package %in% rownames(installed.packages()))
          do.call('library', list(package))

       # if package is not installed locally, download, then load
       else {
          install.packages(package)
          do.call("library", list(package))
       }
   } 
}

path <- function() gsub  ( "\\\\",  "/",  readClipboard ()  )
#Copy path, Panggil function di console
#Copy r path, paste ke var yang diinginkan
```

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message = FALSE}
require("knitr")
opts_knit$set(root.dir = "C:/Users/Fathan/Documents/Obsidian Vault/2. Kuliah/Smt 6/1. Metode Simulasi dan Resampling")
```

@@

# Bab 2

```{r}
x0 <-73 
n <- 250
a <- 17
b <- 7
m <- 1024

xi <- matrix (NA , n, 3 )
colnames (xi) <-c( "aX(i-1)+b", "Xi", "Ui") 
for  (i in 1 :n){
  xi[i,1] <- (a * x0 + b) 
  xi[i,2] <- xi[i, 1]%%m 
  xi[i,3] <- xi[i, 2]/m 
  x0 <- xi[i,2]
}
hist(xi[,3])

cbind("i"=1:20,    "Xi"=xi[1:20,2], 
      "i"=101:120, "Xi"=xi[101:120,2], 
      "i"=201:220, "Xi"=xi[201:220,2])
```

![](images/clipboard-2916962344.png)

```{r}
n <- 1000
x1 <- 0.9
for(i in 2:n) x1[i] <- (pi + x1[i-1])^5%%1

hist(x1)

cbind("i"=1:20,    "Xi"=xi[1:20,2], 
      "i"=101:120, "Xi"=xi[101:120,2], 
      "i"=201:220, "Xi"=xi[201:220,2])
```

## Soal 3.5

```{r, warning=FALSE, message = FALSE}
install_load('readxl','dplyr','kableExtra','DT')
raw.data <- read_xlsx("Data pert 2.xlsx")
data <- raw.data
```
